%===================================== CHAP 7 =================================

\chapter{Project Life Cycle}

\section{Planning and Research}
The group initiated the project with a planning and research phase, lasting from January the 11th to February the 3rd. 

\subsection{Planning}
The importance of the planning phase was emphasised by the group to avoid being forced to start over because the project was insufficient according to what the customer wanted. \\

The planning phase was initiated with thoroughly choose project, focusing on the strengths and weaknesses within the group. To ensure that every member had the same ambitions and a common understating of what the group expected of each other, a group contract was also formulated. This contract has been important for the group dynamic (see apendix X). The risk analysis was also developed during the planning phase, as issues might arise unexpectedly and needs to be managed in a proper fashion (see chapter \ref{riskAnalysis}).  \\  

As the project was assigned - the group prioritised to establish contact with the customer to get a more precise idea of what was to be developed. A contract between the team and the customer was also formulated - ensuring both parties held the same expectations for the project, and of each other during the development process (see apendix X).\\

As the group achieved a better idea of what the project implied - a set of roles were created. These were delegated to the group members depending on prior experience and desire (see chapter \ref{projectOrganisation}).

\subsection{Research}

\subsubsection{Workshop With Users and Providers}

\section{Sprint 0}
The sprint goal for sprint 0 was "Create first design draft, planning and set up product backlog." \\

Sprint 0 did not have any user stories. Instead the sprint was used to set up the workspace, create an index template in Django, create a product backlog with the customer, decided the MVP (see chapter \ref{MVP}), create a first design draft of the application and doing as much planning as possible. The group chose to do it this way, so the development could start already in the beginning of sprint 1. \\

The design draft was drawn as a paper prototype, and the group performed a demonstration to the customer. He was satisfied with the idea, and it created a great discussion about how the group should continue working. \\

Sprint retrospective meeting summary:\\
The group are satisfied with their own efforts. Heaps of work are accomplished, and everyone are motivated to keep working next week. \\
    
The group agrees that they should be more effective in their work sessions, so they can accomplish more. 


\section{Sprint 1}
Problem: customer wanted to use web hotel, we want web server
- Update risk analysis
Discussion: how much time to spend on project, is set meeting times enough or should we work outside meetings?

Sprint backlog, burndowncharts, sprint review

\section{Sprint 2}
Sprint backlog, burndowncharts, sprint review

\section{Sprint 3}
Sprint backlog, burndowncharts, sprint review

\section{Sprint 4}
Sprint backlog, burndowncharts, sprint review

\section{Sprint 5}
Sprint backlog, burndowncharts, sprint review

\cleardoublepage